### 2022-05-30 main/chapter_2ljets.tex
tweaks, Int High > int high

The core idea behind the design of the $\twoljets$-electroweak analysis is to
update the regions of the partial Run~2 search in its $\twoljets$
channel~\cite{atlas_23l_SUSY_2016_24}.
A particular goal was to improve sensitivity by replacing their overlapping
`SR2-Int' and `SR2-High' regions with orthogonal, combined selections.
\emph{I am grateful to Sarah Williams for suggesting this approach.}
As in the $\twoljets$-strong search, each signal region is chosen from an
expected sensitivity for each signal point.
These regions and their resulting exclusion contours are displayed in
Figure~\ref{fig:2ljets_23l_stuff}.

\begin{figure}[tp]
\centering
\begin{subfigure}{0.62\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_23l_sr2inthigh.png}
    \caption{SR2-Int and SR2-High}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.52\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_23l_contours_fig_08d.png}
    \caption{Combined exclusion}
\end{subfigure}
\hfill
\begin{subfigure}{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_23l_chosen_regions.png}
    \caption{Chosen regions}
\end{subfigure}
\caption{%
Figures reproduced from the partial Run~2 search with $2/3\ell$
selections~\cite{atlas_23l_SUSY_2016_24, hepdata.81996}.
\\[0.5em]
(a) Histogrammed distribution of $\met$ in and below SR2-Int and SR2-High with
example signal models.
SR2-Int requires $\met > 150\,\eV[G]$ and SR2-High requires $\met > 250\,\eV[G]$.
The rightmost bin incluedes overflow.
\\[0.5em]
(b) Contours for the combined $\twoljets$ and $3\ell$ channels.
Each signal point chooses a signal region which is displayed in (c).
\\[0.5em]
(c) Signal regions selected for each signal point in the grid.
Two-lepton selections occupy the largest mass splittings.
The $3\ell$ regions are orthogonal and combined.
The separation between SR2-low and $3\ell$ is not trivial.
}
\label{fig:2ljets_23l_stuff}
\end{figure}

% run1
\TODO{run 1?}
\cite{atlas_2l_SUSY_2013_11}

@@

\TODO{sr2 int high figure}

% 2/3l, older 2l context
% update with run 2
% multi-bin fit
% orthogonal regions

>>>>

The core idea behind the design of the $\twoljets$-electroweak analysis is to
update the regions of the partial Run~2 search in its $\twoljets$
channel~\cite{atlas_23l_SUSY_2016_24}.
A particular goal was to improve sensitivity by replacing their overlapping
`SR2-int' and `SR2-high' regions with orthogonal, combined selections.
\emph{I am grateful to Sarah Williams for suggesting this approach.}

As in the $\twoljets$-strong search, the partial Run~2 search chose one
$\twoljets$ signal region from an expected sensitivity for each signal point.
Two regions and the exclusion contours from that search are displayed in
Figure~\ref{fig:2ljets_23l_stuff}/

\begin{figure}[tp]
\centering
\begin{subfigure}{0.62\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_23l_sr2inthigh.png}
    \caption{SR2-int and SR2-high}
\end{subfigure}
\\[0.5em]
\begin{subfigure}{0.52\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_23l_contours_fig_08d.png}
    \caption{Combined exclusion}
\end{subfigure}
\hfill
\begin{subfigure}{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/2ljets_23l_chosen_regions.png}
    \caption{Chosen regions}
\end{subfigure}
\caption{%
Figures reproduced from the partial Run~2 search with $2/3\ell$
selections~\cite{atlas_23l_SUSY_2016_24, hepdata.81996}.
\\[0.5em]
(a) Histogrammed distribution of $\met$ in and below SR2-int and SR2-high with
example signal models.
SR2-int requires $\met > 150\,\eV[G]$ and SR2-high requires $\met > 250\,\eV[G]$.
The rightmost bin includes overflow.
\\[0.5em]
(b) Contours for the combined $\twoljets$ and $3\ell$ channels.
Each signal point chooses a signal region which is displayed in (c).
The grey region shows exclusion from a previous search in Run~1
data~\cite{atlas_2l_SUSY_2013_11}.
\\[0.5em]
(c) Signal regions selected for each signal point in the grid.
Two-lepton selections occupy the largest mass splittings.
The $3\ell$ regions are orthogonal and combined.
The separation between SR2-low and $3\ell$ is not trivial.
}
\label{fig:2ljets_23l_stuff}
\end{figure}

@@
